%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\usepackage{xcolor}
\usepackage{color,soul}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,% hyperlinks will be black
  linkcolor=blue,% hyperlink text will be green
  linkbordercolor=blue,% hyperlink border will be red
}  


% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean
 \usepackage{ifsym}

 \usepackage{expl3}
\expandafter\def\csname ver@l3regex.sty\endcsname{} 
% adjust the page margins
% \usepackage[bottom=0.5in, top=0.5in, scale=0.8, right=1in, left=0.5in]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage[bottom=0.5in, top=0.3in, scale=0.8, right=0.5in, left=0.5in]{geometry}
\usepackage{multicol}

\makeatletter
\Hy@AtBeginDocument{%
  \def\@pdfborder{0 0 1}% Overrides border definition set with colorlinks=true
  \def\@pdfborderstyle{/S/U/W 0.5}% Overrides border style set with colorlinks=true
                                % Hyperlink border style will be underline of width 1pt
}

\RenewDocumentCommand{\section}{sm}{%
  \strut\sectionstyle{#2\hfill}%
  \par\nobreak\addvspace{1ex}\@afterheading
  }

\RenewDocumentCommand{\subsection}{sm}{
  \strut\subsectionstyle{#2}{\color{color1}{\subsectionfill}}%
  \par\nobreak\addvspace{0.5ex}\@afterheading}
%
\makeatother

\renewcommand*{\cvitem}[3][.25em]{%
  \begin{tabular}{@{}p{\maincolumnwidth}@{\hspace{\separatorcolumnwidth}}p{\hintscolumnwidth}@{}}%
    {#3} &\raggedleft\hintstyle{#2}%
  \end{tabular}%
  \par\addvspace{#1}}

% the following definition is from the file moderncvstyleclassic.sty
\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
%   \ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}% I changed this line (with comma) ...
    \ifthenelse{\equal{#4}{}}{}{ {\slshape#4}}% ... into this one (without comma).
    \ifthenelse{\equal{#5}{}}{}{, #5}%
    \ifthenelse{\equal{#6}{}}{}{, #6}%
    \strut%
    \ifx&#7&%
      \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}
%%%



% personal data
\firstname{Andrew}
\familyname{Lloyd}
\title{Full Stack Web Developer} % optional, remove / comment the line if not wanted
\mobile{778 679 8485} % optional, remove / comment the line if not wanted
\email{andrew.lloyd01@googlemail.com} 
\homepage{www.arlmedia.ca} % optional,
\social[github]{andrewrlloyd88}  
\social[linkedin]{andrewlloyd01}   
\address{}{}{\textifsymbol{18} Victoria, BC} % optional, 

\begin{document}
\hypersetup{
  urlcolor=blue,
  urlbordercolor=blue,
  pdfborder={1 1 1},
  pdfborderstyle={/S/U/W 0.5}   
}}
\makecvtitle
\setulcolor{blue}
\vspace{-2.5em}

% section Summary (end)

\section{Technical Toolbelt}
\cventry{}{Frontend:}{React, Redux, JavaScript, HTML5/CSS, NextJS, MaterialUI  SASS, SCSS, Bootstrap, Responsive Design, Storybook}{}{}{}{}{}{}
\cventry{}{Backend:}{Node/Express, Ruby on Rails, PostgreSQL, MongoDB}{}{}{}{}{}{}
\cventry{}{Testing:}{Cypress, Jest, Mocha, Chai, Capybara, CircleCI, PhantomJS, RSpec}{}{}{}{}{}{}
\cventry{}{Other:}{Github, C\#, RESTful API, ERD, Netlify, Heroku, Vercel, FeaturePeek, Agile Methodologies(SCRUM), Draw.io, Figma, Adobe Creative Suite, \LaTeX{}, Unity3D}{}{}{}{}{}{}
\vspace{.25em}
% section Skills (end)
\vspace{.25em}
\section{Projects}

\cventry{}{\href{https://github.com/AndrewRLloyd88/Shoppies-Challenge}{{The Shoppies Movie Awards}}}{}{}{}{Built for the Shopify UX Developer Intern and Web Developer Intern Challenge Summer 2021
\begin{itemize}
\item \textbf{Front End:} React, JavaScript, CSS, MaterialUI
\item \textbf{Back End:} Axios, PostgreSQL, Ruby on Rails
\item \textbf{Deployment:} Heroku and Netlify: \url{https://theshoppies-movie-awards.netlify.app/}
\end{itemize}
}
\vspace{.25em}

\cventry{}{\href{https://github.com/AndrewRLloyd88/National-Logistics-Transportation}{{National Logistics Transportation}}}{}{}{}{Re-design of business website for a Missouri based logistics firm.
\begin{itemize}
\item \textbf{Front End:} React, JavaScript, CSS, MaterialUI
\item \textbf{Deployment:} Netlify: {\underline{\url{https://national-logistics-transportation.netlify.app/}}}
\end{itemize}
}
\vspace{.25em}


\cventry{}{\href{https://github.com/AndrewRLloyd88/ListKeeper}{{ListKeeper}}}{}{}{}{A personal safety app disguiused as a to do list app. Entry for Mintbean's: Social Justice Hack Week.
\begin{itemize}
\item \textbf{Front End:} Next.JS, React, JavaScript, CSS, MaterialUI
\item \textbf{Back End:} MongoDB, Twillio, SendGrid, CircleCI
\item \textbf{Deployment:} Vercel: \url{https://listkeeper.vercel.app/}
\end{itemize}
}
\vspace{.25em}

\cventry{}{\href{https://github.com/AndrewRLloyd88/beat-machine-hackathon}{{BeatJuice}}}{}{}{}{An entry for Mintbean's Campus JavaScript Playoffs: Build a Beat Machine Hackathon.
\begin{itemize}
\item \textbf{Front End:} React, HowlerJS, JavaScript, CSS, MaterialUI
\item \textbf{Deployment:} FeaturePeek: \url{https://dashboard.featurepeek.com/peek/k5zh70zl#/}
\end{itemize}
}
\vspace{.25em}

\cventry{}{\href{https://github.com/AndrewRLloyd88/Hack_the_Quiz_Platform_Hackathon}{{Jeopardy}}}{}{}{}{A quiz app clone of the game show Jeopardy. An entry for Mintbean's Hack the Quiz Platform Hackathon.
\begin{itemize}
\item \textbf{Front End:} React, React Router, Redux , JavaScript, CSS
\item \textbf{Deployment:} Netlify: \url{https://jeopardy-hackathon.netlify.app/}
\end{itemize}
}
\vspace{.25em}

\cventry{}{\href{https://github.com/AndrewRLloyd88/fork_it_all_frontend}{{Forkitall}}}{}{}{}{A Single Page React app that allows users to share their twists on various recipes.
\begin{itemize}
\item \textbf{Front End:} React, React Router, React Bootstrap, Webpack, Babel, SASS
\item \textbf{Back End:} Axios, PostgreSQL, Ruby on Rails
\item \textbf{Deployment:} Heroku: \url{https://fork-it-all.herokuapp.com/}
\end{itemize}
}

\cventry{}{\href{https://github.com/AndrewRLloyd88/scheduler}{{Interview Scheduler}}}{}{}{}{A Single Page React app that allows users to book and cancel interviews.
\begin{itemize}
\item \textbf{Front End:} React, Webpack, Babel, SASS
\item \textbf{Back End:} Axios, PostgreSQL, Express, Webpack Dev Server
\item \textbf{Test:} Jest, Cypress, Storybook
\end{itemize}
}

\vspace{.5em}
% section Projects (end)
\vspace{.25em}
\section{Education}
\cventry{Nov 2020}{{Diploma: Full Stack Web Development}}{Lighthouse Labs - Victoria, BC}{}{}{}
\cventry{Aug 2020}{\href{https://www.udemy.com/course/the-complete-web-development-bootcamp/}{\textit{The Complete 2020 Web Development Bootcamp}}}{Udemy - Online course}{}{}{}
\cventry{July 2020}{{Certificate of Web Development with JavaScript}}{Lighthouse Labs - Victoria, BC}{}{}{}
\cventry{Nov 2014}{MA in Sound Design with Post Production}{University of York, York, UK}{}{}{}
\cventry{Jun 2012}{BA (Hons) Game Design and Media}{Sheffield Hallam University, Sheffield, UK}{}{}{}
% section Education (end)

\newpage

\section{Professional Experience}

\cventry{Nov 2020 - Present}{Freelance Web Developer}{}{}{}{Blue Portal Coding, Remote}
\begin{itemize}
\item Re-design business websites for clients
\item Consult with clients for technical solutions to meet their specific project needs.
\item Utilize analytical and problem-solving skills to improve client's existing codebase.
\end{itemize}

\cventry{Apr 2014 - Present}{Freelance Videographer}{}{}{}{Arlmedia.ca}
\begin{itemize}
\item Worked for various clients to create promotional video media.
\item Oversaw all videography, equipment set up and operation on production shoot sites.
\item Conducted post production duties and video editing using latest post production software.
\end{itemize}

\cventry{Oct 2018 - Aug 2020}{Office Administrator}{}{}{}{St Peter and Paul/St. Matthias Anglican Churches, Victoria, BC}
\begin{itemize}
\item Managed parish offices, created and maintained parish documents and bulletins 
\item coordinated guest rentals
\item Oversaw clerical duties and church communications via website, email and phone.
\end{itemize}

\cventry{Apr 2017 - Jul 2018}{Instructor of Post Sound Production/Sound Recording}{}{}{}{Pacific Design Academy, Victoria, BC}
\begin{itemize}
\item Independently led, organised, directed and delivered a twelve week college syllabus 
\item Instructed on topics such as Adobe Audition, technical audio editing, production recording for film.
\item Increased student standards for audio classes achieving an 80\% average grade.
\end{itemize}

\cventry{Mar 2018 - Jul 2018}{Technical Representative}{}{}{}{Freeman Audio-Visual Canada, Victoria, BC}
\begin{itemize}
\item Configured AV equipment for a number of events at venues
\item Utilized critical thinking skills toubleshooting different audio, video and networking standards.
\item Communicated with clients ensuring their needs were met, guiding them through use of equipment.
\end{itemize}

\cventry{July 2015 - Aug 2016}{Technical QC - Subtitling}{}{}{}{Zoo Digital LTD, Sheffield, UK}
\begin{itemize}
\item Completed quality control testing for subtitle files for clients such as Netflix, HBO, Disney and the BBC. 
\item Audited media for audio and visual consistency as well as working to client specified style guides
\item Assisted QC department to reach a < 1\% rejection rate resulting in securing Netflix as a client.
\end{itemize}

\cventry{July 2015 - Nov 2015}{First Line Support Engineer}{}{}{}{ASK4 LTD, Sheffield, UK}
\begin{itemize}
\item Assisted customers connecting to ASK4 services and solving connection issues with network diagnostics.
\item Learned and utilized in-house network management tools to aid network maintenance.
\item Worked with engineers remotely to guide them through floor plans and technical schematics of servers.
\end{itemize}

\cventry{May 2011 - Sep 2011}{Technical Gesture Designer}{}{}{}{Sumo Digital LTD, Sheffield, UK}
\begin{itemize}
  \item Originated gestures via scripts for Nike+ Kinect training for Xbox360 (released Oct 2012).
  \item Utilized Kinect and development hardware collaborating with senior developers to suggest new tools.
  \item Extensively tested game software and document bugs for Microsoft. Partook in morning scrums with the team.
  \end{itemize}

% section Experience (end)
\end{document}